Dynamic Transition Analysis with TIMES

### 2020-06-25 doc/2020-03-paper/Appendix.tex
adjusted plot width and legends
Former-commit-id: c5e2c31a189fc816638987eebdc40e010fba5b20
Former-commit-id: 86035ec06681e1d9b2daf96a89475c5d4832517a

\begin{table}[!ht]
	\caption{Capacity limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic & 332 \\
Onshore wind & 180 \\
Offshore wind (fixed) & 130 \\
Offshore wind (floating) & 260 \\
Nuclear & 50 (with new tech.) \\
Nuclear & 100 (without new tech.) \\
\gls{PWS} & 100 (without new tech.) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

>>>>

\begin{table}[!ht]
	\caption{Capacity limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic & 332 \\
Onshore wind & 180 \\
Offshore wind (fixed) & 130 \\
Offshore wind (floating) & 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}
